maxent model avec xvalidation

### 2019-04-03 src/stack_test.Rmd
new background dataset
please please please

@@

>>>>

#count number of non-zero coefficients, excluding the final four rows
coefile <- read.csv("../output/maxent/output/mod9foraic/species.lambdas", header = FALSE)
coefile <- head(coefile, -4)
coefile2 <- subset(coefile, V2 > 0 | V2 < 0)
nocoeff <- nrow(coefile2)

@@

from dismo thing... but with my bad code... seems to need to have 
```{r}
# file with presence points
fnames <- list.files(path=paste(system.file(package="dismo"), '/ex', sep=''),
pattern='grd', full.names=TRUE )
predictors <- stack(fnames)
occurence <- paste(system.file(package="dismo"), '/ex/bradypus.csv', sep='')
occ <- read.table(occurence, header=TRUE, sep=',')[,-1]

fold <- kfold(occ, k=5)
occtest <- occ[fold == 1, ]
occtrain <- occ[fold != 1, ]

occtrain <- train2003
occtrainpa <- occtrain$occurrence
occtrain <- subset(occtrain, select = -c(year, occurrence))

me2 <- maxent(x = occtrain, p = occtrainpa, file = .asc, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE"))
me2

occtest <- test2003
occtrain <- train2003
e1 <- evaluate(p= occtrain, a= occtest, me2) #@models[[2]]
e1

pvtest <- data.frame(extract(predictors, occtest))
avtest <- data.frame(extract(predictors, bg))
e2 <- evaluate(me2, p=pvtest, a=avtest)
e2

testp <- predict(me2, pvtest)
testa <- predict(me2, avtest)
e3 <- evaluate(p=testp, a=testa)
e3
threshold(e3)
plot(e3, 'ROC')
